Fractional Types

### 2013-02-23 frac.tex
conclusion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:cat}

The interpretation of {{PiTF}} in the category of sets and relations is
adequate in the sense that it produces a language in which every program is a
reversible relation and in which relations are first-class values. This
relational model is however, unsatisfactory, for several reasons:

@@

Although this semantics appears to have ``better'' properties than the
relational one, we argue that it is not \emph{the} ``perfect'' semantics. By
including the zero vector, the language has
morphisms that do not correspond to isomorphisms and it is difficult to
reconcile the interpretation with the view that the types are rational
numbers. What would really be a ``perfect'' interpretation is one in which we
can only express {{Pi}}-isomorphisms as first class values and in which the
types are interpreted in a way that is consistent with the rational
numbers. Fortunately, there is promising significant work on the groupoid
interpretation of type theory and on the categorification of the rational
numbers that we outline next.

The fundamental idea of both lines of previous work is that it is possible to
build sets (with additional structure) with a \emph{fractional cardinality}.

%% EXPAND on this

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

Give the denotation of a few combinators. The denotation of {{eta_{1+1} }} is
the relation:

{{ {[ (1/(), (left(), left())), (1/(), (right(),right ())) ]} }}

give some intuition; example with eta/epsilon

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:cat}

We have introduced the idea of \emph{fractional types} in the context of a
reversible language founded on type isomorphisms and preservation of
information. Values of fractional types represent \emph{negative
  information}, a concept which is difficult to introduce in a conventional
language that allows arbitrary creation and deletion of information but which
is much simpler to deal with when the surrounding language infrastructure
guarantees preservation of information. Fractional types and values can be
used to express a simple and elegant notion of higher-order functions: a
function {{b1 :-* b2}} is a first-class value consisting of negative
information drawn from {{b1}} and positive information drawn from {{b2}}.

The interpretation of our language {{PiTF}} in the category of sets and
relations is adequate in the sense that it produces a language in which every
program is a reversible relation and in which relations are first-class
values. This relational model is however, unsatisfactory, for several
reasons:

@@

Although this semantics appears to have ``better'' properties than the
relational one, we argue that it is not \emph{the} ``perfect'' semantics. By
including the zero vector, the language has morphisms that do not correspond
to isomorphisms and it is difficult to reconcile the interpretation with the
view that the types are rational numbers. What would really be a ``perfect''
interpretation is one in which we can only express {{Pi}}-isomorphisms as
first class values and in which the types are interpreted in a way that is
consistent with the rational numbers. Fortunately, there is promising
significant work on the groupoid interpretation of type theory and on the
categorification of the rational numbers that we outline next. The
fundamental idea of both lines of previous work is that it is possible to
build sets (with additional structure) with a \emph{fractional cardinality}
--- a topic we are currently investigating in detail.
